Parametric analysis of ambisonic audio

### 2020-06-05 manuscript.tex
wip
modified title and abstract

%\usepackage{hyperref}

@@

%ADD YOUR DATA
\title{Ambisonic domain methods for immersive audio production enhancement}
%\subtitle{\todo{subtitle Required?}}
\author{Author: Andrés Pérez López}

@@

Recent years have witnessed a rise in immersive multimedia content, as a result of the developments in Virtual and Augmented Reality, where spatial audio plays a crucial role for the creation of a realistic experience. 
Ambisonic microphones allow the recording of sound scenes while preserving their spatial characteristics. For that reason, ambisonic has turned into the \textit{de facto} standard for immersive audio transmission. Yet, few production tools exploit all the information available in such media.   
In the present thesis we raise the research question of obtaining relevant information from ambisonic recordings, in a way that is meaningful for producers.
In order to answer the question, we have developed several methods and tools applied to different levels of the immersive sound production workflow; with each of those elements representing a novel contribution to the state-of-the-art in their respective fields.

@@

En els últims anys hem assistit a l'auge del contingut multimèdia immersiu, afavorit pels avanços en Realitat Virtual i Augmentada. En aquest mitjà, el so espacial juga un paper molt important per a la creació d'una sensació de realisme.
Els micròfons ambisonics permeten gravar escenes sonores preservant les seues característiques espacials. A causa d'això, ambisonics s'ha convertit en l'estàndard de facto per a la transmissió d'àudio immersiu. No obstant això, encara son poques les eines de producció que permeten explotar tota la informació disponible en aquest mitjà.
En la present tesi plantegem la pregunta de com obtindre informació rellevant de gravacions ambisonics de manera automàtica, d'una forma que siga significativa per als productors.
Per a això, hem desenvolupat una sèrie de mètodes i eines que s'apliquen a diferents nivells de la cadena de producció de so immersiu; cadascun d'aquests elements representa una contribució nova a l'estat de l'art en aquest camp.

@@

%INSERT CHAPTERS
\input{Chapters/Introduction.tex}
\input{Chapters/ScientificBackground.tex}
\input{Chapters/CoherenceEstimation}
\input{Chapters/ReververationTimeEstimation}
\input{Chapters/SELD}
\input{Chapters/DataGeneration}
\input{Chapters/Conclusions}

>>>>

@@

%ADD YOUR DATA
%\title{Ambisonic domain methods for immersive audio production enhancement}
\title{Parametric analysis of ambisonic audio}
\subtitle{Contributions to methods, applications and data generation}
\author{Author: Andrés Pérez López}

@@

Recent years have witnessed a rise in immersive multimedia content, as a result of the developments in Virtual and Augmented Reality, where spatial audio plays a crucial role for the creation of a realistic experience. 
Ambisonic microphones allow the recording of sound scenes while preserving their spatial characteristics. For that reason, ambisonic has turned into the \textit{de facto} standard for immersive audio transmission. Yet, few production tools exploit all the information available in such media.   
%In the present thesis we raise the research question of obtaining relevant information from ambisonic recordings, in a way that is meaningful for producers.
In the present thesis we raise the research question of obtaining meaningful information from ambisonic recordings, based on the parametric analysis of the sound field.
In order to answer the question we have developed different state-of-the-art methods and tools, which cover a broad range of applications within the parametric audio analysis scope.

% Each of these elements represent a novel contribution to the state-of-the-art in their respective fields.
%In order to answer the question, we have developed several methods and tools applied to different levels of the immersive sound production workflow; with each of those elements representing a novel contribution to the state-of-the-art in their respective fields.

@@

En els últims anys hem assistit a l'auge del contingut multimèdia immersiu, afavorit pels avanços en Realitat Virtual i Augmentada. En aquest mitjà, el so espacial juga un paper molt important per a la creació d'una sensació de realisme.
Els micròfons ambisonics permeten gravar escenes sonores preservant les seues característiques espacials. A causa d'això, ambisonics s'ha convertit en l'estàndard de facto per a la transmissió d'àudio immersiu. No obstant això, encara son poques les eines de producció que permeten explotar tota la informació disponible en aquest mitjà.
En la present tesi plantegem la pregunta de com obtenir informació rellevant de gravacions ambisonics de manera automàtica, basant-nos en l'an\`alisi param\`etric del camp ac\'ustic. 
%d'una forma que siga significativa per als productors.
Per a això, hem desenvolupat una sèrie de mètodes i eines a nivell de l'estat de l'art, 
que cobreixen un ampli espectre d'aplicaciones a l'\`ambit de l'an\`alisi param\`etric del so. 
%que s'apliquen a diferents nivells de la cadena de producció de so immersiu; cadascun d'aquests elements representa una contribució nova a l'estat de l'art en aquest camp.

@@

%INSERT CHAPTERS
\input{Chapters/Introduction.tex}
\input{Chapters/ScientificBackground.tex}
\input{Chapters/ReververationTimeEstimation}
\input{Chapters/CoherenceEstimation}
\input{Chapters/SELD}
\input{Chapters/DataGeneration}
\input{Chapters/Conclusions}
